%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EF Comparative Review CV
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

%%% \documentclass[11pt]{article} % Default document font size
%% \documentclass[11pt]{article} % Default document font size
\documentclass[9pt]{extarticle}

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
%%% \hypersetup{
%%%	pdftitle={Albert Einstein - Curriculum vitae},
%%%	pdfauthor={Albert Einstein}
%%%}

%----------------------------------------------------------------------------------------

\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{center}
{\LARGE\bfseries Oliver Gutsche} % Name
\end{center}


%%% \vspace{0.06\textheight} % Whitespace between contact information and specific CV information

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\subsubsection*{Current Position / Education}

Senior Scientist, joined Fermilab in 2005\\
PhD: 2005, in Physics, University of Hamburg\\
Diploma: 2001, in Physics, University of Hamburg

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

%% \subsubsection*{Employment}

%% \years{1903-1908}Swiss Patent Office, Bern\\
%% \years{1908-1911}University of Bern\\
%% \years{1911-1912}University of Zürich\\
%% \years{1912-1914}Charles University of Prague\\
%% \years{1914-1932}Prussian Academy of Sciences, Berlin\\
%% \years{1920-1930}University of Leiden\\
%% \years{1932-1955}Institute for Advanced Study, Princeton


%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS
%----------------------------------------------------------------------------------------

\subsubsection*{Selected Recent Publications (8 maximum)}

%\cite{HEPSoftwareFoundation:2017ggl}
%\bibitem{HEPSoftwareFoundation:2017ggl}
J.~Albrecht \textit{et al.} [HEP Software Foundation],
``A Roadmap for HEP Software and Computing R\&D for the 2020s,''
Comput. Softw. Big Sci. \textbf{3}, no.1, 7 (2019)
doi:10.1007/s41781-018-0018-8
[arXiv:1712.06982 [physics.comp-ph]].
%141 citations counted in INSPIRE as of 09 Aug 2022

%\cite{HEPSoftwareFoundation:2018xvc}
%\bibitem{HEPSoftwareFoundation:2018xvc}
L.~Bauerdick \textit{et al.} [HEP Software Foundation],
``HEP Software Foundation Community White Paper Working Group - Data Analysis and Interpretation,''
[arXiv:1804.03983 [physics.comp-ph]].
%3 citations counted in INSPIRE as of 09 Aug 2022

%\cite{Bhattacharya:2022qgj}
%\bibitem{Bhattacharya:2022qgj}
M.~Bhattacharya, P.~Calafiura, T.~Childers, M.~Dewing, Z.~Dong, O.~Gutsche, S.~Habib, X.~Ju, M.~Kirby and K.~Knoepfel, \textit{et al.}
``Portability: A Necessary Approach for Future Scientific Software,''
[arXiv:2203.09945 [physics.comp-ph]].
%0 citations counted in INSPIRE as of 09 Aug 2022

%\cite{Cremonesi:2019pdq}
%\bibitem{Cremonesi:2019pdq}
M.~Cremonesi, C.~Bellini, B.~Bian, L.~Canali, V.~Dimakopoulos, P.~Elmer, I.~Fisk, M.~Girone, O.~Gutsche and S.~Y.~Hoh, \textit{et al.}
``Using Big Data Technologies for HEP Analysis,''
EPJ Web Conf. \textbf{214}, 06030 (2019)
doi:10.1051/epjconf/201921406030
[arXiv:1901.07143 [cs.DC]].
%1 citations counted in INSPIRE as of 09 Aug 2022

%\cite{CMS:2016ypc}
%\bibitem{CMS:2016ypc}
V.~Khachatryan \textit{et al.} [CMS],
``Measurements of $t \bar t$ charge asymmetry using dilepton final states in pp collisions at $\sqrt s=8$ TeV,''
Phys. Lett. B \textbf{760}, 365-386 (2016)
doi:10.1016/j.physletb.2016.07.006
[arXiv:1603.06221 [hep-ex]].
%35 citations counted in INSPIRE as of 09 Aug 2022

%\cite{CMS:2018gbj}
%\bibitem{CMS:2018gbj}
A.~M.~Sirunyan \textit{et al.} [CMS],
``Search for dark matter in events with energetic, hadronically decaying top quarks and missing transverse momentum at $ \sqrt{s}=13 $ TeV,''
JHEP \textbf{06}, 027 (2018)
doi:10.1007/JHEP06(2018)027
[arXiv:1801.08427 [hep-ex]].
%61 citations counted in INSPIRE as of 09 Aug 2022

%\cite{CMS:2018zjv}
%\bibitem{CMS:2018zjv}
A.~M.~Sirunyan \textit{et al.} [CMS],
``Search for dark matter produced in association with a Higgs boson decaying to a pair of bottom quarks in proton\textendash{}proton collisions at $\sqrt{s}=13$ TeV,''
Eur. Phys. J. C \textbf{79}, no.3, 280 (2019)
doi:10.1140/epjc/s10052-019-6730-7
[arXiv:1811.06562 [hep-ex]].
%57 citations counted in INSPIRE as of 09 Aug 2022

%\cite{Smith:2020pxs}
%\bibitem{Smith:2020pxs}
N.~Smith, L.~Gray, M.~Cremonesi, B.~Jayatilaka, O.~Gutsche, A.~Hall, K.~Pedro, M.~Acosta, A.~Melo and S.~Belforte, \textit{et al.}
``Coffea: Columnar Object Framework For Effective Analysis,''
EPJ Web Conf. \textbf{245}, 06012 (2020)
doi:10.1051/epjconf/202024506012
[arXiv:2008.12712 [cs.DC]].
%6 citations counted in INSPIRE as of 09 Aug 2022

%----------------------------------------------------------------------------------------
%	SELECTED PROFESSIONAL AWARDS
%----------------------------------------------------------------------------------------

\subsubsection*{Selected Professional Awards (since 2015)}



%----------------------------------------------------------------------------------------
%	ROLES AND RESPONSIBILITIES
%----------------------------------------------------------------------------------------

\subsubsection*{Significant Roles and Responsibilities - Lab and Experiment (since 2015)}

U.S. CMS Software and Computing Operations Program manager (2019 - present)\\
Associate Head of the Scientific Computing Division for CMS, Fermilab (2019 - present)\\
U.S. CMS Software and Computing Operations Deputy Program manager (2016 - 2019)\\
L2 manager for Software and Support in the U.S. CMS Software and Computing Operations Program Execution Team (2016 - 2019)\\
Deputy Head of the Scientific Services Quadrant, Fermilab Scientific Computing Division (2016 - 2019)\\
CMS Offline \& Computing Project Focus Area Lead for Infrastructure and Resources, CMS experiment (2015 - 2019)\\
L2 manager for Operations in the Software and Computing Operations Program Execution Team (2014 - 2016)\\
Assistant Head of the Scientific Computing Division for Science Operations and Workflows, Fermilab (2014 - 2016)

\subsubsection*{Significant Roles and Responsibilities - HEP Community (since 2015)}

Fermilab’s Scientific Advisory Council (2015 - 2016)\\
Editorial board of the journal for “Computing and Software for Big Science” published by Springer (2017 - present)\\
Fermilab’s Users Executive Committee (2018 - 2020)\\
Co-Editor of the American Physics Society (APS) Division of Particles and Fields (DPF) white paper as input to the European Particle Physics Strategy Update 2018 – 2020, responsible for the computing section (2018 - 2018) \\
Organizer of the Computing \& Machine Learning parallel session at The CPAD Instrumentation Frontier Workshop 2018 “New Technologies for Discovery IV” (2018 - 2018)\\
IRIS-HEP Steering Board (2019 - present)\\
WLCG Management Board (2019 - present)\\
WLCG Overview Board (2019 - present)\\
WLCG Collaboration Board (2019 - present)\\
Openscience Grid Council (2019 - present)\\
Fermilab’s Wilson Fellowship hiring committee (2019 - 2022)\\
Co-lead of the Computational Frontier of the Particle Physics Snowmass 2021 process (2020 - 2022)

%----------------------------------------------------------------------------------------
%	MENTORING
%----------------------------------------------------------------------------------------

\subsubsection*{Recent Students and Postdocs Mentored}

2011-2016: Jacob Linacre, Fermilab Research Associate CMS\\
2015-2021: Matteo Cremonesi, Fermilab Research Associate CMS\\
2018-present: Nick Smith, Fermilab Research Associate CMS\\
2019-present: Fernanda Psihas, Fermilab Research Associate SBN, DUNE\\
2020-present: Martin Kwok, Fermilab Research Associate CMS

%----------------------------------------------------------------------------------------

\newpage

\end{document}
